In classical game theory, agents are assumed to be fully rational.
Bounded rationality studies scenarii where agents have limited computation power or make mistakes~\cite{rubinstein:1998}.
In the economics literature, bounded rationality is used to take into account human nature and to explain discrepancies with experiments.
Fully rational agents can perfectly use any knowledge they have about the problem they face.
For example, in a stochastic game of imperfect information, fully rational agents propagate beliefs accurately.
Propagating beliefs means doing Bayesian inference on a belief space whose size increases with time.
Engineered agents have limited computation power, limited memory, and bounded precision.
Furthermore, adaptivity requires the use of local and therefore incomplete information.
As a result, there is no hope to build fully rational adaptive agents in a dynamic world.
In the proposed research, the bounded rationality of engineered agents is used as an advantage.
Instead of relying on propagation of beliefs regarding the imperfect information, simple consistent models are used.
A model is consistent if the agent does not observe evidence contradicting it.

Four approaches using bounded rationality to lower the complexity of the problem are presented below.
The first one uses Kalman filtering to update a model while the others use the notion of consistency.
All the consistency approaches use exogenous models, whereas the proposed research lifts that restriction.
Other differences with the proposed research are highlighted.

\subsection{Linear Modeling}
Chang, Ho and Kaelbling used modeling to simplify multiagent learning~\cite{chang_ho_kaelbling:2004}.
Each agent assumes that the signal received is generated from a linear system and uses Kalman filtering to get the best estimate of the current state.

\subsection{Mean-field Games}
Lasry and Lions studied a setting where a very large number of agents faces identical copies of an \ac{mdp}~\cite{lasry_lions:2007}.
The \acp{mdp} are coupled through a common signal received by the agents.
This signal is the proportion of agents in each state; it is a stochastic process impacted by the strategies of all the agents.
Agents compute their optimal strategies by considering a consistent, exogenous and stationary model of the signal.
Agents are in a \ac{mfe} if their optimal strategies induce precisely this stationary signal.
The goal of \acp{mfe} is to simplify the analysis of games with a very large number of agents.
The main result in the \ac{mfe} literature is that when the number of agents goes to infinity, \acp{mfe} coincide with Nash equilibria.
The fact that the signal is not truly stationary nor exogenous washes away when the number of agents is large.
\acp{mfe} aim at simplifying the analysis of Nash equilibria for a specific game with a large number of players.
The proposed research aims for a different equilibrium concept in general games with any number of players.
Furthermore, \acp{mfe} focuses on stationary models, whereas the proposed research considers more elaborate models.
Weintraub, Benkard, and van Roy applied the mean-field methodology to approximate subgame-perfect equilibria in a problem of dynamic imperfect competition~\cite{weintraub_benkard_van-roy:2008}.
They named their equilibrium concept oblivious equilibrium.

\subsection{Incomplete Theories}
Eyster and Piccione analyzed a scenario in which traders have exogenous nonstationary consistent models of prices on the stock market; these models are called incomplete theories~\cite{eyster_piccione:2011}.
The traders use their theories to acquire assets.
The key result is that traders with more complete theories do not necessarily perform better.
The main difference with the proposed research is that, the actions of the traders do not influence prices.
Therefore, prices are truly exogenous; traders do not need to update their models.

\subsection{Egocentric Modeling}
Seah and Shamma analyzed a specific game where two agents share a one-dimensional signal~\cite{seah_shamma:2008}.
The signal is stochastic and influenced by the strategies of the agents.
However, the agents model it with a consistent stationary exogenous model.
Similarly, in the proposed research, an inaccurate  simplified model is used to lower the complexity of computations.
