The objective of the proposed research is to develop the framework of \acp{eee} in stochastic games and to design decentralized controllers using learning in that framework.
The goal is to enable a set of agents to control a dynamical system in a decentralized fashion.
To do so, the agents play a stochastic game crafted such that its equilibria are decentralized controllers for the dynamical system.
Unfortunately, there exists no algorithm to compute equilibria in stochastic games.
One explanation for this lack of results is the full-rationality requirement of game theory.
In the case of stochastic games, full rationality imposes that two requirements be met at equilibrium.
First, each agent has a perfect model of the game and of its opponents' strategies.
Second, each agent plays an optimal strategy for the \ac{pomdp} induced by its opponents' strategies.
Both requirements are unrealistic.
An agent cannot know the strategies of its opponents; it can only observe the combined effect of its own strategy interacting with its opponents'.
Furthermore, \acp{pomdp} are intractable; an agent cannot compute an optimal strategy in a reasonable time.
In addition to these two requirements, engineered agents cannot carry perfect analytical reasoning and have limited memory; they naturally exhibit bounded rationality.
In the proposed research, bounded rationality is not seen as a limitation and is instead used to relax the two requirements.
In the \ac{eee} framework, agents formulate low-order empirical models of observed quantities called mockups.
Mockups have unmodeled states and dynamic effects, but they are statistically consistent; the empirical evidence observed by an agent does not contradict its mockup.
Each agent uses its mockup to derive an optimal strategy.
Since agents are interconnected through the system, these mockups are sensitive to the specific strategies employed by other agents.
In an \ac{eee}, the two requirements are weakened.
First, each agent has a consistent mockup of the game and the strategies of its opponents.
Second, each agent plays an optimal strategy for the \ac{mdp} induced by its mockup.
The \ac{eee} framework provides a new solution concept for stochastic games.
This solution concept has been contrasted to other classical notions.
General conditions for the existence of \acp{eee} have been derived.
The properties of \acp{eee} will be investigated.
The \ac{eee} framework will be used to solve decentralized control problems through the design of an algorithm converging to \acp{eee}.
